---
title: "Data Visualization"
author: "Joshua Ogundairo"
date: "1/28/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(tseries)

```


## Data Manipulation and visualization



```{r cars}

visual_data <- X2019_Statistical_Bulletin_Public_Finance_Statistics_Final_e_Copy

visual_data <- visual_data[-c(1, 26 : 31) ,]
View(visual_data)
transposed_data <- t(as.vector(visual_data))
View(transposed_data)
attach(as.data.frame(transposed_data))

attach(test_data)

```

# Simple plots

```{r}
# ggplot(data = transposed_data) + geom_histogram(mapping = aes(x = ))

head(test_data)

table(test_data$NRR)

ggplot(data = test_data) + geom_bar(mapping = aes(x = NRR))
ggplot(data = test_data) + geom_histogram(mapping = aes(x = EEE_Full))
```

## How to choose basic plots for variables

There are basically 2 types of variables: Categorical, and Continuous variables. The choice of plots/charts depebnds on which type of variable is under consideration. basic plots for categorical variable is the barplot while basic plot for continuous variable is the histogram.

Each of Eastern, North West & Central, Scotland's Rail, Southern, and Wales & Western will have their individual bars that will plot/show their magnitude.


# An example of visualization problem

> How does people use the season ticket across the regions?
> What region uses Full tickets the most?


### Solution of first question

Variables involved: Region (NRR), Season ticket (EEE_Season)
type of these variables: Categorical, Continuous
what plot/chart to use: 

```{r}
# The plot

ggplot(data = test_data) + geom_point(mapping = aes(x = NRR, y = EEE_Season))

```


Variables involved: Region (NRR), Full ticket (EEE_Full)
type of these variables: Categorical, Continuous
what plot/chart to use: 

```{r}

ggplot(data = test_data) + geom_point(mapping = aes(x = NRR, y = EEE_Full))
```

```{r}

pie(x = NRR)

```

